Self-assembly of colloid-cholesteric composites provides a route to switchable optical materials

### 2014-03-04 trunk/papers/2012-sandwich/response.txt

Dear Dr Huang,

many thanks for sending us the referee reports on our manuscript, 
"Self-assembly of colloid-cholesteric composites: A route to switchable 
optical materials". We are glad that both referees found our work interesting.
We are also grateful for the suggestions for improvement, all of which
we have now implemented in the revised version. We hope the revised
manuscript can now be accepted for publication in Nature Communication.

With best wishes,

K. Stratford, O. Henrich, J. S. Lintuvuori, M. E. Cates and D. Marenduzzo

------------------------------------------------------------------

Point by point response to referees' comments

Reply to Reviewer #1:

COMMENT:
"The authors describe the results of a study of colloidal particles dispersed
in cholesteric blue phases (BP) focusing on the effects of particle
concentration and distribution. Additionally
effects of confinement and external fields are investigated. The use of the
lattice Boltzmann approach allows to follow dynamics after the thermal
quench and electric field application. The
study is an important step in modeling of BPs and should deserve a
publication in Nature Communications. Nevertheless there are some weak
points that need improvement before the publication.
Below is the list of remarks."

RESPONSE:
We thank the reviewer for her/his generally encouraging comments, and for
recommending publication in Nature Communication subject to the resolution
of some points. Below are our detailed reply to each of the reviewer's
question, together with a description of how the comment has been dealt with
in the revision.

COMMENT:
"The term colloid is by the definition a dispersion of particles in a fluid.
Using the term also for the particles my lead to a confusion. In the
manuscript often also a more appropriate word
colloidal particle is used."

RESPONSE: We have standardised on "colloidal particle(s)" or simply
"particle(s)" where appropriate.

COMMENT:
"It would be important to add comments that would help experimentalist in
designing experiments with colloidal blue phases and perhaps stimulate
development of applications on the base of
these materials."

RESPONSE: The issue of experimental guidance is addressed in detail
in our reply to reviewer 2 below. In particular we have added a full
paragraph in the discussion (page 3, highlighted in red), with explicit 
reference to experimental studies on nanoparticle liquid crystal composites 
(currently Refs. [34-39]).

COMMENT:
"Page 2: In the discussion of the physical understanding of trapping of colloidal particles in BP disclination networks it would be useful to refer to the
initial study by Ravnik et al. in Faraday
Discussions 2009 devoted to this topic."

RESPONSE: Citation for Ravnik et al Faraday Discuss. 2010 (sic) is added
[current reference 16].

COMMENT: "250 K is more than the total mesophase stability range!"

RESPONSE: A stability range for templated blue phases of -125 to
+125 degrees Celsius is reported by Castles et al. Nat. Mat. 2012.
We have made this connection more clear by rewriting the relevant
sentence, which now reads (see page 2, highlighted in red): 
"However, recent advances in formulation have widened
this stability range enormously [11,12,13,14]. Most recently,
templated blue phases with a stability range of -125 to 125$^\circ$C
have been reported [Castles], paving the way to applications of BPs
in operational display devices."

COMMENT: The statement "This is defined such that W > 0 gives preferential
perpendicular orientation of the director field at the particle surface." is
not consistent with the interaction form
described in the Supplement.

RESPONSE: We agree this statement was confusing. It has been replaced by
a clearer statement (on page 4, highlighted in red): 
"The anchoring strength is defined such that
W > 0 imparts a preferred orientation to the director field at the
particle surface. This orientation can be either normal to the
surface or in a plane tangential to the surface, a property related
to surface chemistry in experimental systems but which can be imposed
at will in simulations."

COMMENT:
"For potential readers it would be useful to specify the particle radius in
nanometers in the main text. How it compares to the nematic correlation
length? How the radius influences the structures? How tiny the particles can 
still be that the method based on the Landau-de Gennes free energy is 
justified."

RESPONSE: We have added in the main text (last paragraph introduction) a
summary of the relevant dimensions in physical units:  "The simulations
presented here are representative of a liquid crystal blue phase with unit
cell size in the range of 100--500~nm and particles with a radius of
around 50~nm." This new paragraph also serves the requirement for a brief
summary of the results as set out in the manuscript checklist.

RESPONSE (cont.): As a coarse-grained description of the mesophase, the
Landau-de Gennes  theory is appropriate as long as the size of the
colloidal particle is much larger than the size of the mesogen,
the latter being typically in the range of 1--10 nanometres. Our
simulations meet this criteria (particle size about 50 nm) and the
use of Landau-de Gennes is therefore justified.

COMMENT: "Is WR/K = 2.8 justified for nanoparticles used in the study?"

RESPONSE: The choice of WR/K = 2.3 in the simulations (not 2.8)
is used to separate clearly a strong anchoring regime from a
weak anchoring regime (w = 0.23). While typical experimental
values for particles of this size may mean the weak regime is
more common, we do not see that this precludes interest in a
strong anchoring regime.

COMMENT: "Page 4:
Can the G elastic modulus be estimated for modeled structures?"

RESPONSE: We note we did have, in the original manuscript, a
paragraph which discusses estimates of the elastic modulus G
based on analogy with experimentally observed systems. To the
existing paragraph we have appended:
"This figure is consistent with an estimate obtained by comparing
the mechanical properties of the network of defects stabilised by
colloidal particles with those of rubber [Ramos et al 2002] for
the relevant simulation parameters (see Supplementary Information)."
To the supplementary information we append: "For a Frank elastic
constant of $K = 70$~pN and unit cell sizes in the range
$\lambda =$100--500~nm, a corresponding shear modulus $G \simeq
K/\lambda^2 =$0.3--7~kPa." The relevant reference is added.

COMMENT: "Page 5:
Can annealing of the structures obtained with the thermal quench lead to
ordered colloidal structures?"

RESPONSE: Our results suggest that this is probably not the case,
although it is difficult to systematically explore all the possible
quench protocol. That said, our data suggest that even starting with
colloidal particles randomly dispersed in an *ordered* blue phase
particles are able to distort the structure (see Fig. 1A, 1B); this
suggests that time evolution if anything may lead to more disorder,
rather than order.

COMMENT: "Is also in case of the disordered structures observed a change in the
stability range of the colloidal BPs?"

RESPONSE: Determining the stability range of the composite
phases was beyond the scope of this paper. This would have required 
an optimisation of the pitch length, which requires a large number 
of additional simulations for each individual parameter set.

COMMENT:
"In the discussion of colloidal particles in BP thin layers it would be good
to comment the study of Ravnik et al. in Soft Matter 2011 devoted 
the ordered structures of such a system."

RESPONSE: A citation for Ravnik et al (2011) has been added [current
reference 26].

COMMENT:
"Page 6: It would be good to comment the difference between structures in the 
bulk and thin layer for particles with strong anchoring. Does this depend on the
visualization or is more behind?"

RESPONSE: We have added the following at the end of the section
describing the confined geometry: "The degree of similarity between
the bulk and confined structures is somewhat masked by the local
change in particle density in the confined case. If one allows for
this, Figs.~1 and~2 show the individual structural motifs are actually
rather similar: templated lines for weak anchoring and clusters for
strong anchoring."

RESPONSE (cont.): One potential visualisation ambiguity is that the
displayed box sizes are different in each of the figures (cf. particle
size). An explicit statement has been added to each caption to make
this more clear to the reader. ADD CAPTIONS?

COMMENT:
"Are the electric field induced changes irreversible only in case of
colloidal dispersions?"

RESPONSE: For the given parameters the field induced changes are only
irreversible when colloids with sufficiently strong 
anchoring conditions are present. The mesophase without colloids 
undergoes a reversible ordering transition as described in reference [10].

COMMENT: "Page 7 Reference 2 has a mistake."

RESPONSE: The correct punctuation in the page numbers has been
inserted in the reference for Wright and Mermin [current reference 9].

COMMENT: "Supplement Segment 4.2:
The statement "Wall anchoring is either normal or planar with W=K = 1 in
simulation units" is unclear."

RESPONSE: This text has been replaced by a statement which is
transparent: "For both normal and planar anchoring at the walls,
the value of $W$ is the same as that used for the
strongly anchoring particles."

COMMENT:"References of the Supplement:
There are mistakes in references 1 and 2."

RESPONSE: Reference 1, Wright and Mermin, was correct in
the original supplement. Reference 2 has been updated to reflect
the 2nd edition of de Gennes and Prost, which now appears in the
main text [current reference 34].
CHECK REFERENCE

------------------------------------------------------------------------

Reply to Reviewer 2

COMMENT:
"This paper, "Self-assembly of colloid-cholesteric composites: A route to
switchable optical materials" reports simulations of the formation of
particle networks in a cholesteric host and in
particular in the blue phase of the cholesteric host. It reports the
influence of various physical parameters and in particular the surface
anchoring and concentration of the colloidal
particles. The paper also reports how external fields can be employed to
change the morphology of these colloidal composites and how this may be
employed in practical optical devices.

The paper builds on a body of previous research, both theoretical and
experimental that has explored the effects of dispersing particles in a
liquid crystal host. The novelty of the paper is
to model the effect of particles in the blue phases of a cholesteric host
ahd to postulate how these colloids may be employed in specific
applications.

@@

I am not a theorteical physiscist and therefore will not comment on the
methodology but rather will take the perspective of an experimentalist and
how useful this paper is in understanding
these materials and more importantly how useful the paper is in suggesting
and designing experimental procedures and developing the actual materials.

The paper provides insight into the effectiveness of including particles
into the blue phase as a means of controlling and adjusting the structure
and stability of the materials. The paper
is clearly written and the figures, paricularly the included 3D videos,
provide clear perspective on the modeled phases of these materials. The
results are of interest and useful to experimentalists working in the field. "

RESPONSE:
We are grateful to the reviewer for her/his overall positive view of our
work. We also found her/his comments constructive and useful to improve
our paper. We have addressed them as follows.

COMMENT:
"The paper would be even more useful if it included references to actual 
materials, both the liquid crystal host and the added particles and perhaps
even suggested a model system that would be a good starting point to study
experimentally. "

RESPONSE: 
"We have fully taken this point on board.
In a new paragraph in the discussion section, we include six
new references specifically aimed at recent studies on experimental
nanoparticle liquid crystal composites. These are currently [34-39].
The paragraph also discusses the issue of a model system, and suggests
properties such a system may have to help match experiment and simulation."

COMMENT:
"In a similar vein, it would also be useful to address the
practical issue of reproducibility, which has been a major problem 
with these materials. The theoretical results clearly indicate how important 
the formation conditions are to the final result.

What is the authors sense of how easy it will be to reproducibly fabricate a 
device with a specific morphology and optical properties. This seems a likely
practical issue particularly with the rich variety of structures reported in
the simulations."

RESPONSE: Clearly the issue of experimental reproducibility is a difficult
one to be addressed by, of necessity idealised, simulation. However, one
point our simulations do show is that careful characterisation of not
only the particles and host fluid is required, but also of possible
confinement effects and associated anchoring conditions. This we also
address in our updated discussion, see the full paragraph highlighted in
red on pages 7-8.

Authors' note:

* ADDITIONAL CHANGES TO MEET FORMAT REQUIREMENTS
  cf Manuscript checklist

A number of other rearrangements have taken place to meet the
format requirements as set out the manuscript checklist.

Title

- The title has been adjusted to remove punctuation

Authors

- The full postal address has been added
- The corresponding author has been identified (Marenduzzo).

Abstract

- The abstract has been shorted to meet the 150 word limit.
  Citations have been removed to the main text.

Main text

- Symbols and units have been adjusted in places to come into style.

Results

- Subheadings of < 60 characters have been added

- References to supplementary items have been adjusted to come into style.

Methods

- All "methods" material (originally in supplementary information) is now
contained within the main paper. This includes relevant references.

- Dividing subheadings of < 60 characters have been added.

References

- Formatting is adjusted to come into style.

End notes

- A statement of author contributions has been added.

- A statement on conflicts of interest has been added.

Legends

- Figure legends have been adjusted to include a brief title.

Tables

- A title has been included.

### 2014-03-04 trunk/papers/2012-sandwich/CholColloids.tex
updated text (Davide)
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2325 40876441-3496-0410-a613-a2fca35b2ae2

\title{Self-assembly of colloid-cholesteric composites: A route to switchable optical materials}
\author{K. Stratford$^{*}$, O. Henrich$^{*}$, J.~S. Lintuvuori$^{*}$,\\
M. E. Cates, D. Marenduzzo \\ 
{\small SUPA, School of Physics and Astronomy, Edinburgh University,} \\
\small{Edinburgh, EJ9 3JZ, UK}\\
\small{$^{*}$ equally contributed to this work}}
\date{}

@@

{\bf Colloidal particles dispersed in liquid crystals can form new materials with tunable elastic and electro-optic properties~\cite{stark}. In a host comprising  a periodic `blue phase' chiral liquid crystal~\cite{mermin}, the particles should template into colloidal crystals \cite{miha} with potential uses in photonics, metamaterials, and transformational optics~\cite{lavrentovich}. 
Here we show by computer simulation that colloid/cholesteric mixtures can give rise to a much wider range of soft-solid composites than previously anticipated. These include regular crystals, glasses, percolating gels, isolated clusters, twisted rings and undulating colloidal ropes. The final structure can be tuned via the particle concentration, and by varying the surface interactions of the cholesteric host with both the colloids and any confining walls. 
Remarkably, we find that many of these new materials are metastable: two or more structures can arise under identical thermodynamic conditions. The observed structure depends not only on the formulation protocol,
but also on the history of an applied electric field.  
This new class of soft materials should thus be relevant to the design of switchable, multistable devices for optical technologies including, for example, smart glass and e-paper~\cite{epaper}.}

When spherical colloidal particles are mixed into a nematic liquid crystal, 
they disrupt the orientational order in the fluid and create defects (disclination lines) in the nematic close to their surfaces. To minimize the free energy cost, it is generally advantageous for defects to be shared:
therefore the colloidal particles have a generic tendency to aggregate. Such aggregates may further 
self-assemble into lines~\cite{wiresmiha}, 2D crystals~\cite{zumer}, 
planar structures~\cite{tanaka}, or 3D amorphous glasses~\cite{tiffany}.
Besides being of fundamental interest to materials science, these
structures may have tunable elastic and optical properties~\cite{stark}. Hence 
they offer exciting prospects for applications as biosensors~\cite{abbott}, or
as new devices~\cite{colloiddevice,tanakanatmat}.

But one may also choose to disperse colloidal particles in a cholesteric, 
rather than nematic, liquid crystal. The molecules making up this material are
chiral, and this causes their average orientation (described by a director field) to rotate in space in
a helical fashion, rather than remain uniform as in nematics. 
This typically creates a 1-dimensional periodic structure, called the cholesteric phase, whose wavelength 
is the pitch, $p$. The periodicity can however become fully three dimensional in the so-called blue phases (BPs)~\cite{mermin}. BPs arise because the director field can twist around more than one direction at once (see 
the cartoon in Fig. S1). Such double twist 
regions (generally cylinders: DTCs) are energetically favoured at high enough molecular chirality, but
lead to geometric frustration because it is impossible to tile the whole 3D
space with DTCs without also introducing ``disclination lines'' 
(These are singular topological defects on which the director field is 
undefined.) In blue phases these disclination lines themselves either form a 3D periodic regular lattice (in so called BPI and BPII), or remain disordered (BPIII)~\cite{bp3}. 
%
BPs are stabilised by the tendency of chiral molecules to twist, but destabilised by the cost of forming topological defects (which locally diminish the molecular alignment). In conventional cholesteric materials~\cite{mermin} this balance is only achievable in a narrow temperature range of a few degrees, around the onset of liquid crystalline ordering. However, recent advances in formulation have widened this stability range enormously (up to 250K) paving the way to
applications of BPs in display devices~\cite{kikuchi,bplasers,coleswidetrange,bpdevice,coles}.

Besides being remarkable materials in themselves, BPs offer significant promise as hosts for dispersing colloidal particles. Because BPs contain a disclination network even in the absence of
particles, they can potentially template colloidal self-assembly. 
This was proved recently by simulations of BP-dispersed nanoparticles which 
exclude the surrounding liquid crystal but otherwise have negligible surface 
interaction with it (to give a so-called `weak anchoring' regime)~\cite{miha}. 
Such particles are attracted to the disclination network in BPs: by covering up the defect cores, the high elastic energy cost of those regions is avoided. The pre-existing order of the defect network then templates particles into a regular colloidal crystal of the same periodicity. 
Because this structure has a wavelength in the visible range, 
the resulting material should inherit (and likely enhance) the incomplete photonic bandgap of the parent blue phase, as exploited for instance in laser devices~\cite{bplasers}; for related possibilities see \cite{lavrentovich}.

A second compelling reason to study colloid-BP composites is that, even without particles, BPs can show several competing metastable free energy minima,
corresponding to different topologies of the defect network~\cite{adriano,fukuda}, with a strong dependence on applied electric or magnetic fields~\cite{henrichfield}.
% 
Adding particles is likely to further enrich the free energy landscape, creating composites that might be promising candidates for bistable or multistable devices, in which energy is needed only to switch optical properties and not to maintain them. (This is the e-paper paradigm~\cite{epaper}, and can lead to huge energy savings.)
To explore such metastability, and switching strategies between states, we require multi-unit-cell, time-dependent simulations. These go beyond previous studies of colloid-BP composites~\cite{miha} but follow comparable simulations of pure BPs~\cite{bp3,henrichfield,domaingrowth}, and isolated and dimeric colloids in cholesterics~\cite{juho1,juho2}. Our methodology and simulation parameters are summarized in the Supplementary Information.

We show in Fig.~1 A-D the final state structures of four simulations in which we first equilibrated a stable BPI disclination network in bulk (with periodic boundary conditions) and then dispersed colloidal particles at random within it. Among dimensionless control parameters are the colloid volume fraction $\phi$  ($\phi = 1\%$ or $5\%$); the ratio $r = R/\lambda$ of particle radius to the BP lattice parameter $\lambda$ (here $r\simeq 0.14$) and the ratio $w = WR/K$ where $W$ is the anchoring strength of the cholesteric at the particle surface, and $K$ is the elastic constant of the liquid crystal. (This is defined such that $W>0$ gives preferential perpendicular orientation of the director field at the particle surface.) For the latter we choose $w = 0.23, 2.3$ which are within typical experimental range~\cite{tiffany}. This parameter can be viewed as the ratio of the anchoring energy, $WR^2$, to the elastic energy scale for distortion $KR$.

For a single colloidal particle in a nematic fluid, $w$ controls the formation of a local topological defect at the particle surface~\cite{stark}, with weak distortion of the nearby fluid at small $w$. In the colloid-BP system, $w$ also plays a determining role in the final composite structure. When $w$ is small (Fig.~ 1A,B; Suppl. Movie 1,2), the attraction of particles to the disclination lattice causes
 the lattice to become covered by particles, with little disruption of its
 long-range order. Thus a templated colloidal crystal is created, as first reported in~\cite{miha}. Interestingly, the weak but finite anchoring apparently creates an elastic force between the colloids which leads to very slow dynamics (Fig. S4) and the formation of small colloidal lines within disclinations, especially for dilute samples (Fig. 1A). It seems likely that polymer-stabilised  blue phases~\cite{kikuchi} work by a similar principle to this small $w$ case, with a weak segregation of monomers towards the defect regions.

For large $w$ (Fig.~1C,D; Suppl. Movie 3,4), the picture changes dramatically.
Each colloidal particle now disrupts significantly the order of the nearby fluid, with defect formation close to its surface~\cite{stark}. The resulting strong disruption of local liquid crystalline order around each particle leads now to 
a strong interparticle attraction. This restructures the disclination
network completely, destroying the long range order of
the original BPI topology. Most notably, particle aggregation favours
the formation of defect junctions, where four disclinations meet. This structural motif is present in the unit cell of BPII rather than BPI (and also seen in the amorphous BPIII~\cite{bp3}). The particle clusters are disjoint at low volume fractions ($\phi\simeq 1\%$) but they interact elastically via the connecting disclinations. At larger $\phi$, the aggregates join up to form a percolating colloidal cluster which essentially templates the disclinations rather than vice versa.

As colloid-nematic composites~\cite{tiffany}, all the structures in Fig.~1A-D 
should be soft solids, of nonzero elastic 
modulus $G$ at low frequency. This contrasts with pure BPs, where
$G=0$ as the fluid can flow with a finite
viscosity via permeation of molecules through a fixed defect lattice~\cite{permeation1,permeation2}. We expect the
structures in Fig.~1A-C to be only weak gels, as here the 
defect network percolates but particle contacts do not. This is broadly similar to the cholesteric-nanoparticle gel reported
in~\cite{lubensky} (with $G<1$ Pa). In contrast, the colloidal gel
structure in Fig.~1D should be much more resistant mechanically, 
due to the formation of a thick percolating particle network. The 
structure is now akin to that of the self-quenched glass found in 
colloid-nematic composites~\cite{tiffany} at much higher volume 
fraction (over 20\% as opposed to below 5\% here), for which $G\sim 10^3$ Pa.

A more practical protocol for including particles in a BPI phase is to disperse the particles at random in an isotropic phase, and then quenching this into the temperature range where BPI is stable. Here we know that, without particles, the kinetics can favour disordered (BPIII-like) intermediates which may be long lived or even metastable~\cite{domaingrowth}. Fig.~1E-H shows outcomes of such a quench protocol with the same parameter sets as in Fig.~1A-D. For small $w$, the particles again decorate the disclination lines, but are this time templated onto an amorphous network rather than an ordered one.
Increasing the volume fraction (Fig.~1F) leads to a more even coverage with
a better defined particle spacing. 
For large $w$, on the other hand, strong interparticle forces again dictate
the self-assembly. At low concentrations, discrete particle clusters decorate an amorphous defect lattice (Fig.~1G) whereas at higher $\phi$ a percolating network of colloid strands (the gel in Fig.~1H) is again seen. 
The structures in Fig. 1A-H have been followed for $\sim$20 ms 
(see Fig. S4); they correspond to either very slowly evolving states or 
deep metastable minima (elastic interactions are of
order $KR$ and dwarf thermal motion, see
Fig. S4 and Ref.~\cite{stark,lavrentovich}).

In display devices and other optical applications, it is typical for liquid crystals to be strongly confined (and subject to strong boundary effects), in contrast to the bulk geometries considered above. We therefore next describe how colloidal suspensions self assemble in thin sandwiches (thickness $h = 1.75 \lambda$), whose confining walls can favour either tangential (planar degenerate) or normal (homeotropic) orientation of the director field. For simplicity we here impose one or the other as a strict boundary condition.

Fig.~2A-D shows the case of normal wall anchoring on varying $\phi$ and $w$. We quench from the isotropic to the ordered phase as was done in Fig.~1E-H, and again find a metastable, amorphous disclination network (see Supplementary Information). The resulting colloid-cholesteric composites are somewhat similar to those seen in the bulk: for small $w$ the particles are templated by the network (Fig.~2A,B), whereas for large $w$ we observe isolated clusters (Fig.~2C) and percolated colloidal gels (Fig.~2D), for $\phi = 1\%$ and $4\%$ respectively. There are, however, significant effects of the confining walls.
First, the normal anchoring at the wall recruits particles there,  giving (for the chosen $h$) a density enhancement of the colloids at both walls 
(see side-views in Fig.~2A-D). Second, the clusters formed at large $w$ are themselves anisotropic with an oblate habit. These clusters
are similar to those reported experimentally for large colloids in a
cholesteric (but non-BP) host~\cite{niek}.

>>>>

\title{Self-assembly of colloid-cholesteric composites provides
a route to switchable optical materials}

\author{K. Stratford$^{*}$, O. Henrich$^{*}$, J.~S. Lintuvuori$^{*}$,\\
M. E. Cates, D. Marenduzzo$^\dagger$ \\ 
SUPA, School of Physics and Astronomy, The King's Buildings,\\
The University of Edinburgh, Edinburgh, EH9 3JZ, UK\\
\small{$^{*}$ equally contributed to this work}\\
\small{$^\dagger$ Corresponding author: dmarendu@ph.ed.ac.uk}
}
\date{}

@@

\noindent

%% ABSTRACT 150 WORDS MAX NO REFERENCES
\noindent
{\bf
Colloidal particles dispersed in liquid crystals can form new materials
with tunable elastic and electro-optic properties. In a periodic `blue
phase' host, particles should template into colloidal crystals with
potential uses in photonics, metamaterials, and transformational optics.
Here we show by computer simulation that colloid/cholesteric mixtures can
give rise to regular crystals, glasses, percolating gels, isolated clusters,
twisted rings and undulating colloidal ropes. This structure can be tuned
via particle concentration, and by varying the surface interactions of the
cholesteric host with both
the particles and confining walls. Many of these new materials are metastable:
two or more structures can arise under identical thermodynamic conditions.
The observed structure depends not only on the formulation protocol, but also
on the history of an applied electric field. This new class of soft materials
should thus be relevant to design of switchable, multistable devices for
optical technologies such as smart glass and e-paper.
}
%% EXACTLY 150

\bigskip
\noindent
%% [Introduction: Max 1000 words; we have about 650]

\noindent
When spherical colloidal particles are mixed into a nematic liquid crystal, 
they disrupt the orientational order in the fluid and create defects (disclination lines) in the nematic close to their surfaces. To minimize the free energy cost, it is generally advantageous for defects to be shared:
therefore the colloidal particles have a generic tendency to aggregate. Such aggregates may further 
self-assemble into lines~\cite{wiresmiha}, 2D crystals~\cite{zumer}, 
planar structures~\cite{tanaka}, or 3D amorphous glasses~\cite{tiffany}.
Besides being of fundamental interest to materials science, these
structures may have tunable elastic and optical properties~\cite{stark}. Hence 
they offer exciting prospects for applications as biosensors~\cite{abbott}, or
as new devices~\cite{colloiddevice,tanakanatmat}.

But one may also choose to disperse colloidal particles in a cholesteric, 
rather than nematic, liquid crystal. The molecules making up this material are
chiral, and this causes their average orientation (described by a director field) to rotate in space in
a helical fashion, rather than remain uniform as in nematics. 
This typically creates a 1-dimensional periodic structure, called the cholesteric phase, whose wavelength 
is the pitch, $p$. The periodicity can however become fully three dimensional in the so-called blue phases (BPs)~\cite{mermin}. BPs arise because the director field can twist around more than one direction at once (see 
the cartoon in Supplementary Fig.~1). Such double twist 
regions (generally cylinders) are energetically favoured at high enough molecular chirality, but
lead to geometric frustration because it is impossible to tile the whole 3D
space with double twist cylinders without also introducing ``disclination lines'' 
(These are singular topological defects on which the director field is 
undefined.) In blue phases these disclination lines themselves either form a 3D periodic regular lattice (in so called BPI and BPII), or remain disordered (BPIII)~\cite{bp3}. 
%
BPs are stabilised by the tendency of chiral molecules to twist, but destabilised by the cost of forming topological defects (which locally diminish the molecular alignment). In conventional cholesteric materials~\cite{mermin} this balance is only achievable in a narrow temperature range of a few degrees, around the onset of liquid crystalline ordering.
\textcolor{red}{
However, recent advances in formulation have widened this stability
range enormously~\cite{kikuchi,bplasers,coleswidetrange,bpdevice}. Most
recently, templated BPs with a stability range of -125
to~125$^\circ$C have been reported \cite{coles}, paving the way to
applications of BPs in operational display devices.}

Besides being remarkable materials in themselves, BPs offer significant promise as hosts for dispersing colloidal particles. Because BPs contain a disclination network even in the absence of
particles, they can potentially template colloidal self-assembly. 
This was proved recently by simulations of BP-dispersed nanoparticles which 
exclude the surrounding liquid crystal but otherwise have negligible surface 
interaction with it (to give a so-called `weak anchoring' regime)~\cite{extrareference1,miha}. 
Such particles are attracted to the disclination network in BPs: by covering up the defect cores, the high elastic energy cost of those regions is avoided. The pre-existing order of the defect network then templates particles into a regular colloidal crystal of the same periodicity. 
Because this structure has a wavelength in the visible range, 
the resulting material should inherit (and likely enhance) the incomplete photonic bandgap of the parent blue phase, as exploited for instance in laser devices~\cite{bplasers}; for related possibilities see \cite{lavrentovich}.

A second compelling reason to study colloidal-BP composites is that, even without particles, BPs can show several competing metastable free energy minima,
corresponding to different topologies of the defect network~\cite{adriano,fukuda}, with a strong dependence on applied electric or magnetic fields~\cite{henrichfield}.
% 
Adding particles is likely to further enrich the free energy landscape, creating composites that might be promising candidates for bistable or multistable devices, in which energy is needed only to switch optical properties and not to maintain them. (This is the e-paper paradigm~\cite{epaper}, and can lead to huge energy savings.)
To explore such metastability, and switching strategies between states, we require multi-unit-cell, time-dependent simulations. These go beyond previous studies of colloidal-BP composites~\cite{miha} but follow comparable simulations of pure BPs~\cite{bp3,henrichfield,domaingrowth}, and isolated and dimeric colloidal particles in cholesterics~\cite{juho1,juho2}.

\textcolor{red}{
The simulations presented here are representative of a liquid crystal
blue phase with unit cell size in the range of 100--500~nm \cite{mermin},
and particles with a diameter of around 50~nm. The simulations
address both the bulk structure, and the structure which forms when
the colloidal dispersion is confined in a narrow sandwich of width
comparable to the unit cell size~\cite{extrareference2}. It is seen
that a wide variety of structure is possible, and may be influenced
by parameters including the solid volume fraction, and the details
of the anchoring at the colloid surface (and the at the surface of the
confining walls). Further, evidence is found for metstable switching of
this structure in an applied electric field. Details of the
computational approach are set out in the Methods section, while
simulation parameters are reported in the Supplementary Information.
}

\bigskip
\noindent
\textbf{\large Results}

\noindent
\textbf{Structure in bulk BPI.}
We show in Fig.~1 A-D the final state structures of four simulations in which we first equilibrated a stable BPI disclination network in bulk (with periodic boundary conditions) and then dispersed colloidal particles at random within it. Among dimensionless control parameters are the particle solid volume fraction $\phi$  ($\phi = 1\%$ or $5\%$); the ratio $r = R/\lambda$ of particle radius to the BP lattice parameter $\lambda$ (here $r\simeq 0.14$) and the ratio $w = WR/K$ where $W$ is the anchoring strength of the cholesteric at the particle surface, and $K$ is the elastic constant of the liquid crystal.
\textcolor{red}{
The anchoring strength is defined such that $W > 0$ imparts a preferred
orientation to the director field at the particle surface. This orientation
can be either normal to the surface or in a plane tangential to the surface,
a property related to surface chemistry in experimental systems.% but which
%can be imposed at will in simulations.
We choose} $w = 0.23, 2.3$ which are within typical experimental range~\cite{tiffany}. This parameter can be viewed as the ratio of the anchoring energy, $WR^2$, to the elastic energy scale for distortion $KR$.

For a single colloidal particle in a nematic fluid, $w$ controls the formation of a local topological defect at the particle surface~\cite{stark}, with weak distortion of the nearby fluid at small $w$. In the colloidal-BP system, $w$ also plays a determining role in the final composite structure. When $w$ is small (Fig.~ 1A,B; Supplementary Movies~1 and~2), the attraction of particles to the disclination lattice causes
 the lattice to become covered by particles, with little disruption of its
 long-range order. Thus a templated colloidal crystal is created, as first reported in~\cite{miha}. Interestingly, the weak but finite anchoring apparently creates an elastic force between the colloidal particles which leads to very slow dynamics
(Supplementary Fig.~4) and the formation of small colloidal lines within disclinations, especially for dilute samples (Fig. 1A). It seems likely that polymer-stabilised  blue phases~\cite{kikuchi} work by a similar principle to this small $w$ case, with a weak segregation of monomers towards the defect regions.

For large $w$ (Fig.~1C,D; Supplementary Movies~3 and~4), the picture changes
dramatically.
Each colloidal particle now disrupts significantly the order of the nearby fluid, with defect formation close to its surface~\cite{stark}. The resulting strong disruption of local liquid crystalline order around each particle leads now to 
a strong interparticle attraction. This restructures the disclination
network completely, destroying the long range order of
the original BPI topology. Most notably, particle aggregation favours
the formation of defect junctions, where four disclinations meet. This structural motif is present in the unit cell of BPII rather than BPI (and also seen in the amorphous BPIII~\cite{bp3}). The particle clusters are disjoint at low volume fractions ($\phi\simeq 1\%$) but they interact elastically via the connecting disclinations. At larger $\phi$, the aggregates join up to form a percolating colloidal cluster which essentially templates the disclinations rather than vice versa.

As colloidal-nematic composites~\cite{tiffany}, all the structures in
Fig.~1A-D 
should be soft solids, of nonzero elastic 
modulus $G$ at low frequency. This contrasts with pure BPs, where
$G=0$ as the fluid can flow with a finite
viscosity via permeation of molecules through a fixed defect lattice~\cite{permeation1,permeation2}. We expect the
structures in Fig.~1A-C to be only weak gels, as here the 
defect network percolates but particle contacts do not. This is broadly similar to the cholesteric-nanoparticle gel reported
in~\cite{lubensky} (with $G<1$ Pa). In contrast, the colloidal gel
structure in Fig.~1D should be much more resistant mechanically, 
due to the formation of a thick percolating particle network. The 
structure is now akin to that of the self-quenched glass found in 
colloidal-nematic composites~\cite{tiffany} at much higher volume 
fraction (over 20\% as opposed to below 5\% here), for which $G\sim 10^3$ Pa.
\textcolor{red}{
This figure is consistent with an estimate obtained by comparing
the mechanical properties of the network of defects stabilised by
colloidal particles with those of rubber~\cite{ramos} for
the relevant simulation parameters (see Supplementary Information).}

A more practical protocol for including particles in a BPI phase is to disperse the particles at random in an isotropic phase, and then quenching this into the temperature range where BPI is stable. Here we know that, without particles, the kinetics can favour disordered (BPIII-like) intermediates which may be long lived or even metastable~\cite{domaingrowth}. Fig.~1E-H shows outcomes of such a quench protocol with the same parameter sets as in Fig.~1A-D. For small $w$, the particles again decorate the disclination lines, but are this time templated onto an amorphous network rather than an ordered one.
Increasing the volume fraction (Fig.~1F) leads to a more even coverage with
a better defined particle spacing. 
For large $w$, on the other hand, strong interparticle forces again dictate
the self-assembly. At low concentrations, discrete particle clusters decorate an amorphous defect lattice (Fig.~1G) whereas at higher $\phi$ a percolating network of colloidal strands (the gel in Fig.~1H) is again seen. 
The structures in Fig. 1A-H have been followed for $\sim$20 ms 
(see Supplementary Fig.~4); they correspond to either very slowly evolving
states or  deep metastable minima (elastic interactions are of
order $KR$ and dwarf thermal motion, see
Supplementary Fig.~4 and Ref.~\cite{stark,lavrentovich}).

\medskip
\noindent
\textbf{Structures in confined BPI.}
In display devices and other optical applications, it is typical for liquid crystals to be strongly confined (and subject to strong boundary effects), in contrast to the bulk geometries considered above. We therefore next describe how colloidal suspensions self assemble in thin sandwiches (thickness $h = 1.75 \lambda$), whose confining walls can favour either tangential (planar degenerate) or normal (homeotropic) orientation of the director field. For simplicity we here impose one or the other as a strict boundary condition.

Fig.~2A-D shows the case of normal wall anchoring on varying $\phi$ and $w$. We quench from the isotropic to the ordered phase as was done in Fig.~1E-H, and again find a metastable, amorphous disclination network (see Supplementary Information). The resulting colloidal-cholesteric composites are somewhat similar to those seen in the bulk: for small $w$ the particles are templated by the network (Fig.~2A,B), whereas for large $w$ we observe isolated clusters (Fig.~2C) and percolated colloidal gels (Fig.~2D), for $\phi = 1\%$ and $4\%$ respectively. There are, however, significant effects of the confining walls.
First, the normal anchoring at the wall recruits particles there,  giving (for the chosen $h$) a density enhancement of the colloid particles at both walls 
(see side-views in Fig.~2A-D). Second, the clusters formed at large $w$ are themselves anisotropic with an oblate habit. These clusters
are similar to those reported experimentally for large colloid particles in a
cholesteric (but non-BP) host~\cite{niek}.
